Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-03-04 article-models-tt.tex
remark on internalizing valid inference rules

>>>>

We would also like to remark explicitly that the valid judgments of the original type
theory become contexts, families or terms, depending on what kind of judgments
it was. Then, valid inferences of the original type theory become valid
judgments here. In some sense, the theory we present here is therefore a second
order theory over the basic theory of types.
